working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
edits

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="Effect sizes for the 10 different species. The different families appear with different colours, when a species was focal was coloured differently from its family."}

@@

#SOME
load("effect_size_species/all_effect_size.RData")

#BROL
load("effect_size_species/brol_effect_size.RData")
p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = margin(t=0, l=0))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,0.5),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")

#BRRA
load("effect_size_species/brra_effect_size.RData")
pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,0.5,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "B)")

#ERSA
load("effect_size_species/ersa_effect_size.RData")
p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,0.5,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "C)")+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))

#SIAL
load("effect_size_species/sial_effect_size.RData")
p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,0.5,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "D)")

#IPAQ
load("effect_size_species/ipaq_effect_size.RData")
p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+geom_point(alpha=c(1,1,1,1,1,0.5,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "E)")

#IPPU
load("effect_size_species/ippu_effect_size.RData")
p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
  theme(axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,0.5,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "F)")

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")

#SOLY
load("effect_size_species/soly_effect_size.RData")
p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,0.5,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "I)")

@@

p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,alpha=c(0.5,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "J)")

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="Effect sizes for the 10 different species. The different families appear with different colours, when a species was focal was coloured differently from its family."}

@@

load("effect_size_species/all_effect_size.RData")

#BROL
load("effect_size_species/brol_effect_size.RData")
p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text( hjust=0),title = element_text(vjust=2),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("A) B. oleracea")

#BRRA
load("effect_size_species/brra_effect_size.RData")
pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("B) B. rapa")

#ERSA
load("effect_size_species/ersa_effect_size.RData")
p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))+ggtitle("C) E. sativa")

#SIAL
load("effect_size_species/sial_effect_size.RData")
p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("D) S. alba")

#IPAQ
load("effect_size_species/ipaq_effect_size.RData")
p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("E) I. aquatica")

#IPPU
load("effect_size_species/ippu_effect_size.RData")
p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("F) I. purpurea")

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("G) C. annuum")

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("H) P. integrifolia")

#SOLY
load("effect_size_species/soly_effect_size.RData")
p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("I) P. integrifolia")

@@

p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("J) P. integrifolia")
